A recipe for extremely reproducible enrichment analysis (and why we need it)

### 2023-12-08 manuscript/manuscript.Rmd
closer to submission

Although this reproducibility study is relatively small, there are a few key observations.
We observe that only 4/20(20%) of studies achieved a high degree of reproducibility.
In a way, this is unexpected, given the simplicity of using DAVID.
Users provide a list of gene idetifiers in a text box and select some options.
There are several posible explanations for this inconsistency:

@@

The problem of bioinformatic resources becoming unavailable is not a new one, being thoroughly describes a decade ago [@Hennessey2013-tj].
We are worried that a reliance on web tools can leave researchers in violation of their data management responsibilities, as preservation mandates include software as well as original research data [@NHMRC2019-wu ; @Harvard_2023-cl ].

@@

Publicly available data were obtained from Digital Expression Explorer 2 (dee2.io).
Expression data from untreated and Aza treated AML3 cells.
Accession Number SRP038101.

Data are available under the terms of the GNU General Public License v3.0.

>>>>

Although this reproducibility study is relatively small, there are a few key observations.
We observe that only 4/20(20%) of studies achieved a high degree of reproducibility.
In a way, this is unexpected, given the simplicity of using DAVID.
Users provide a list of gene identifiers in a text box and select some options.
There are several posible explanations for this inconsistency:

@@

The problem of bioinformatic resources becoming unavailable is not a new one, being thoroughly described a decade ago [@Hennessey2013-tj].
We are worried that a reliance on web tools can leave researchers in violation of their data management responsibilities, as preservation mandates include software as well as original research data [@NHMRC2019-wu ; @Harvard_2023-cl ].

@@

Publicly available data were obtained from Digital Expression Explorer 2 (dee2.io).
Expression data from untreated and Aza treated AML3 cells.
NCBI Sequence Read Archive accession Number SRP038101.
